msb106_assignment

### 2024-01-17 msb106_assignment.qmd
hvv

>>>>

```{r}
data1 <- arbeidskraft <- read_csv("arbeidskraft.csv") |> 
  select(arbeidsvekst = OBS_VALUE, geo, deg_urb, TIME_PERIOD)

data2 <- arbeidsledighet1 <- read_csv("arbeidsledighet1.csv") |> 
  select(arbeidsledig = OBS_VALUE, geo, deg_urb, TIME_PERIOD)

data3 <- huspris <- read_csv("huspris.csv") |> 
  select(huspris = OBS_VALUE, geo, deg_urb, TIME_PERIOD)
```

```{r}
arbeidsvekst <- data1 %>%
  mutate(deg_urb = case_when(
    deg_urb == "DEG1" ~ "Cities",
    deg_urb == "DEG2" ~ "Towns/Suburbs",
    deg_urb == "DEG3" ~ "Rural Areas",
    TRUE ~ as.character(deg_urb)  # Beholder andre verdier uendret
  ))
```

```{r}
arbeidsledige <- data2 |> 
  mutate(deg_urb = case_when(
    deg_urb == "DEG1" ~ "Cities",
    deg_urb == "DEG2" ~ "Towns/Suburbs",
    deg_urb == "DEG3" ~ "Rural Areas",
    TRUE ~ as.character(deg_urb)  # Beholder andre verdier uendret
  ))
```

```{r}
huspris <- data3 |> 
  mutate(deg_urb = case_when(
    deg_urb == "DEG1" ~ "Cities",
    deg_urb == "DEG2" ~ "Towns/Suburbs",
    deg_urb == "DEG3" ~ "Rural Areas",
    TRUE ~ as.character(deg_urb)  # Beholder andre verdier uendret
  ))
```

```{r}
join <- arbeidsvekst |> 
  left_join(arbeidsledige, join_by(geo, TIME_PERIOD, deg_urb))

join1 <- join |> 
  left_join(huspris, join_by(geo, TIME_PERIOD, deg_urb))

maindata <- join1 |> 
  left_join(data, join_by(geo, TIME_PERIOD, deg_urb))
```
